The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-29 outputs/docs/events/paper.Rmd
Update paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(kableExtra)
library(knitr)
library(tidyverse)

elections <-
  read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())

governments <-
  read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())

keyEvents <-
  read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())

significances <-
  read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())

top_words <-
  read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols()) %>% 
  rename(Topic = topic, Terms = terms)

hansard_sources <-
  read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

elections_results <-
  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Significant)

governments_results <-
  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Party,-`Died in Office`,-Significant)

key_events_results <-
  read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols()) %>%
    select(-Expected)

key_events_results_cols <-
  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 sitting periods over the period 1901 to 2017 inclusive.

@@

>>>>

```{r setup, include = FALSE}
# install.packages("here")
library(here)
# install.packages("kableExtra")
library(kableExtra)
# install.packages("knitr")
library(knitr)
# install.packages("tidyverse")
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

library(readr)

elections <-
  read_csv("../../../inputs/misc/misc_elections_data.csv", col_types = cols())

governments <-
  read_csv("../../../inputs/misc/change_of_pm.csv", col_types = cols())

keyEvents <-
  read_csv("../../../inputs/misc/key_events.csv", col_types = cols())

significances <-
  read_csv("../../../outputs/misc/significance.csv", col_types = cols())

top_words <-
  read_csv2("../../../outputs/results-topic_models_and_gammas/top_words_80.csv", col_types = cols()) %>% 
  rename(Topic = topic, Terms = terms)

hansard_sources <-
  read_csv("../../../outputs/misc/hansard_sources.csv", col_types = cols())

elections_results <-
  read_csv("../../../outputs/results-analysis_model/results-elections.csv", col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Significant)

governments_results <-
  read_csv("../../../outputs/results-analysis_model/results-governments.csv", col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Party,-`Died in Office`,-Significant)

key_events_results <-
  read_csv("../../../outputs/results-analysis_model/results-outliers.csv", col_types = cols()) %>%
    select(-Expected)

key_events_results_cols <-
  read_csv("../../../outputs/results-analysis_model/results-outliers_in_columns.csv", col_types = cols())

@@

Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM. We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 822 sitting periods over the period 1901 to 2017 inclusive. Appendix \@ref(wastonywrong) contains more information about the sitting patterns over time.

@@

# Sitting periods over time {#wastonywrong}

TBD
